Paper_Figure

### 2023-11-03 paper_figure.Rmd
path adjustment

---
title: "Paper_Figure"
output: pdf_document
date: '2023-10-16'
---
# Load Data & Preprocess
```{r}
library("Seurat")
path <- "/data/ruiqi/local_marker/dataset/tabular_muris/"
tissue_name = "marrow_facs"
tiss <- readRDS(sprintf("%s%s.rds",path,tissue_name))

@@

ggsave(filename = "supfig-bonemarrow.png", plot = p, width = 8, height = 5, dpi = 300)
# 
# centroids <- aggregate(. ~ cell_label, data = as.data.frame(Embeddings(tiss, "tsne")), FUN = mean)
# p <- DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + theme_void() + NoLegend() + ggtitle("Bone Marrow FACS")
# p = p + 
#   geom_text_repel(data = centroids, aes(x = tSNE_1, y = tSNE_2, label = cell_label, color = cell_label),
#                    box.padding = 0.3, point.padding = 0.3, segment.color = 'grey50',max.overlaps = 100)
```

# Fig - Pipeline
```{r}
source("./LMD_function.R", echo = F)

@@

P_ls = Obtain_Pls(W = W, max_time = 2^10)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = visual_space)
ggsave(filename = "fig-pipeline1.png", plot = p, width = 6, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^10,2^15)
p = Visualize_score_pattern(res, genes = genes, add_point = check_time)

ggsave(filename = "fig-pipeline2.png", plot = p, width = 8, height = 5)

# Check Gene Diffusion on Cell graph by time
pl = lapply(1:length(genes),function(i){
  gene = genes[i]
  FeaturePlot_diffusion(coord = visual_space,init_state = rho[gene,],P_ls = P_ls,W = W,check_time = check_time,gene_name = gene,gene_color = scales::hue_pal()(2)[i])
})
p = as.ggplot(pl[[1]]) / as.ggplot(pl[[2]] & labs(title = NULL))
ggsave(filename = "fig-pipeline3.png", plot = p, width = 16, height = 8)
```

@@

# Set the color code for all methods
method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_default","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(9, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
path = "./benchmark_result/"
tissue_ls = c("marrow_facs","pancreas_facs","lung_facs")
df_auc = do.call(rbind,lapply(tissue_ls,function(tissue_name){df = read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE); df$'Tissue' = tissue_name; df}))

df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1 - CellMarkerDB","Criterion2 - MaxFC")
df_auc$Tissue = factor(df_auc$Tissue,levels = tissue_ls)
levels(df_auc$Tissue) = c("Bone Marrow","Pancreas","Lung")
# Create the plot
fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 3) +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method]) + facet_wrap(~gt_set)
fig = fig + theme(
          legend.title = element_text(size = 20),
          legend.text = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          panel.grid = element_blank(),
          axis.line = element_line(colour = "black"),
          panel.background = element_blank(),
          strip.background = element_rect(fill = "white", color = "white") ,
          strip.text = element_text(size = 15, color = "black"))

ggsave(filename = "fig-known_marker_comparison.png", plot = fig, width = 10, height = 5)
```

<!-- # Fig - Enrichment Overlap of Prioritized Genes with CellMarker Database Confidence Markers -->
<!-- ```{r} -->
<!-- path = "./benchmark_result/" -->
<!-- tissue_name = "marrow_facs" -->

<!-- library(Seurat) -->
<!-- cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>%  -->
<!--   filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>%  -->
<!--   filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) -->

<!-- df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv")) -->

<!-- method = "lmd" -->
<!-- gene_bin = data.frame(gene = rownames(df_benchmark)[order(df_benchmark[,method])][1:1000]) -->
<!-- gene_bin$freq = unlist(lapply(gene_bin$gene,function(i){ -->
<!--   id = which(grepl(paste0("^", i, "$"), cell_marker_db$gene_name1, ignore.case = TRUE) + grepl(paste0("^", i, "$"), cell_marker_db$gene_name2, ignore.case = TRUE) >=1) -->
<!--   return(length(id)) -->
<!-- }) ) -->
<!-- gene_bin$'freq_class' = cut(gene_bin$freq, breaks = c(-Inf,1,3,Inf), labels = c("none", "low", "high"), right = FALSE) -->

<!-- gene_bin$bin <- cut(seq(1:nrow(gene_bin)), breaks = 40, labels = FALSE) -->
<!-- gene_bin$'bin_label' = paste0(nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin-1)+1,"-",nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin)) -->
<!-- gene_bin$'bin_label' = factor(gene_bin$'bin_label',levels = unique(gene_bin$'bin_label')) -->

<!-- gene_freq_prop <- gene_bin %>% -->
<!--   group_by(bin_label, freq_class) %>% -->
<!--   summarise(n = n()) %>% -->
<!--   mutate(freq = n / sum(n)) -->
<!-- gene_freq_prop$freq_class = factor(gene_freq_prop$freq_class,levels = c("none","low","high"),labels = c("None(=0)","Low(1,2)","High(>=3)")) -->

<!-- coldef = setNames(c("gray71","firebrick1","firebrick4"),levels(gene_freq_prop$freq_class)) -->

<!-- fig = ggplot(gene_freq_prop, aes(fill=freq_class, y=freq, x=bin_label)) + -->
<!--   geom_bar(position="fill", stat="identity") + -->
<!--   ylab("Frequency") + -->
<!--   xlab("Gene Rank") + -->
<!--   labs(fill = "Confidence") + -->
<!--   scale_fill_manual(values= coldef) + -->
<!--   theme_minimal() +  -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) -->

<!-- fig -->
<!-- ``` -->
<!-- ```{r} -->
<!-- genes = c("Ctla2a","Fpr2","Mmp8") -->
<!-- pl = lapply(genes,function(g) FeaturePlot(tiss, g, order = TRUE) + labs(color = "Expression") + ggtitle(sprintf("%s (rank %d)",g,which(gene_bin == g)))) -->
<!-- fig = cowplot::plot_grid(plotlist = pl, ncol = 3) -->
<!-- fig -->
<!-- ``` -->

# Fig - Gene Ranking Variations between LMD and Other Methods
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
# df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
#   paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
# })
g = c("Cd19","Naaa","Mogat2","Tifa","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
names(g) = rep(method_vs_set,each = 2)
pl = lapply(1:length(g),function(i){
  x = g[i]
  subtitle = sprintf("%s:%d, %s:%d",method_fullname[method_vs],df_label_all[x,method_vs],method_fullname[names(g)[i]],df_label_all[x,names(g)[i]])
  color_label = ifelse(df_label_all[x,method_vs] > df_label_all[x,names(g)[i]],"red","blue")
  FeaturePlot(tiss,features = x,order =TRUE) + labs(color = "Expression") + labs(title = x,subtitle = subtitle) + 
    theme(
      plot.title = element_text(face="bold", size = 30,color = color_label),
      plot.subtitle = element_text(size = 20),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      axis.line = element_blank())
  # + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
pl = pl[order(seq(length(g))%%2,decreasing = TRUE)]
pl[[1]] = pl[[1]] + labs(y = "Favored by LMD") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "blue"))
pl[[(length(pl)/2)+1]] = pl[[(length(pl)/2)+1]] + labs(y = "Favored by Other methods") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "red"))

@@

ggsave(filename = "fig-ranking_comparison2.png", plot = fig, width = 25, height = 10)
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  fullmethod = method_fullname[method]
  fullmethodvs = method_fullname[method_vs]
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = fullmethod
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = fullmethodvs
  df_label$'color' = as.factor(df_label$'color')
  rank_cor = cor(log(df_label[,1:2],10))[1,2]
  colnames(df_label)[1:2] = c("x","y")
  p = ggplot(df_label, aes(x=x, y=y,color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red","blue","grey50"),
                     breaks = c(fullmethod,fullmethodvs),
                     labels = c("Favored by LMD","Favored by Other methods")) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + 
    scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) + 
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), 
         y = paste0(method_fullname[method_vs]," Rank"),
         color = "Highlighted Genes",
         title = paste("cor =", round(rank_cor, 2)))
  # annotate gene labels
  p = p + ggrepel::geom_text_repel(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label),min.segment.length = unit(0, 'lines'),nudge_y = -0.5,show.legend = FALSE,size = 5)
  p = p + theme(
    plot.title = element_text(size = 15),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
})
for(i in 2:length(pl_rank)){
  pl_rank[[i]] <- pl_rank[[i]] + theme(axis.title.y=element_blank())
}
p = (wrap_plots(pl_rank,nrow = 1) & theme(legend.position="bottom")) + plot_layout(guides = "collect")

@@

# Fig - Density Index
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"
score_measure = read.table(paste0(path,tissue_name,"_density_index.csv"),header = TRUE)
score_measure$Method = ifelse(score_measure$Method %in% names(method_fullname),method_fullname[score_measure$Method],score_measure$Method)

@@

line_type = replace(coldef,names(coldef),"solid")
line_type["Seurat v3 Wilcoxon unfiltered"] = "twodash"
line_type["All genes"] = "dashed"

fig = ggplot(score_measure %>% filter(Method!="All genes"), aes(x = TopGene, y = DensityIndex, color = Method, group = Method, linetype = Method),linewidth = 2) + 
  geom_line(lwd = 1) +
  scale_x_log10(breaks = 10^(2:4), labels = expression(10^2, 10^3, 10^4)) +
    # expand_limits(x = c(50, 10^4)) +
  geom_hline(aes(yintercept = baseline, color = "All genes", linetype = "All genes")) +
  scale_color_manual(values= c(coldef[names(coldef)%in%score_measure$Method],"All genes" = "black")) + 
  scale_linetype_manual(values = line_type) +
  theme(
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
  # geom_text_repel(data = score_measure %>%  filter(Method!="all genes") %>% group_by(Method) %>% slice_head(n = 2) %>% slice_tail(n = 1), aes(label = Method), hjust = 0)

ggsave(filename = "fig-densityindex.png", plot = fig, width = 8, height = 5)
```

@@

pl = lapply(list(jaccard_index,jaccard_index_droplet),function(mtx){
  jaccard_index_pruned = mtx[ct_selected,module_selected]
  colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
  Visualize_jaccard_mtx(jaccard_index_pruned)
})
titles = c("FACS","Droplet")
pl <- lapply(1:length(pl), function(i){pl[[i]] + labs(title = titles[i]) + theme(plot.title = element_text(size = 20, face = "bold"))})
p = wrap_plots(pl,ncol = 2) + plot_layout(guides = "collect")
ggsave(filename = "supfig-ct-specific-module3.png", plot = p, width = 10, height = 8)
```
# Fig - Cell Cycle
## Annotate CC
```{r}
cell_cycle = read.csv("./marrow_result/annotated_cell_cycle.csv")[["Phase"]]
tiss$'Phase' = cell_cycle
p1 = DimPlot(tiss,group.by = "Phase", cols = c("grey",scales::hue_pal()(3)[2:3])) + labs(title = "Phase annotated by Seurat",color = "Phase") + theme(
  axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.line = element_blank())
p = wrap_plots(p1,(wrap_plots(pl_module[c(16,17,18,31,32)],ncol = 3) & theme(plot.title = element_text(size = 15))) + plot_layout(guides = "collect"),nrow = 1,design = "AABBB")

ggsave(filename = "fig-module-cellcycle.png", plot = p, width = 3*5, height = 3*2)
```
## Reactome enrichment
```{r}
df = read.csv("./marrow_result/reactome_pathway_cc.csv")
df$module = as.factor(df$module)
df$GeneRatio = as.numeric(df$Count / table(gene_partition)[df$module])
df$Description = factor(df$Description, levels = names(sort(table(df$Description))))
levels(df$Description)[6] = "HDR through Homologous Recombination\n or Single Strand Annealing (SSA)"
p = ggplot(df, aes(x=module, y=Description)) +
  geom_point(aes(size=GeneRatio, color=p.adjust), alpha=0.7) +
  scale_color_gradientn(colors=colorRampPalette(c("red", "blue"))(99), name="p.adjust") +
  theme_minimal() +
  labs(size="Gene Ratio") +
  theme(legend.position="right",
        axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
      axis.text.y = element_text(size = 10),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15))
ggsave(filename = "fig-module-cellcycle2.png", plot = p, width = 10, height = 6)
```

>>>>

---
title: "Paper_Figure"
author: "Ruiqi Li"
output: pdf_document
date: '2023-10-16'
---
# Load Data & Preprocess
```{r}
library("Seurat")
# tissue_name = "marrow_facs"
# tiss <- readRDS(sprintf("%s%s.rds",path,tissue_name))
tiss <- readRDS("processed_facs_Marrow_srat.rds")
tiss_droplet <- readRDS("processed_droplet_Marrow_srat.rds")

@@

ggsave(filename = "supfig-bonemarrow.png", plot = p, width = 8, height = 5, dpi = 300)
```

# Fig - Pipeline
```{r}
source("LMD_function.R", echo = F)

@@

P_ls = Obtain_Pls(W = W, max_time = 2^15)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = visual_space)
ggsave(filename = "fig-pipeline1.png", plot = p, width = 6, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^10,2^15)
p = Visualize_score_pattern(res, genes = genes, add_point = check_time)

ggsave(filename = "fig-pipeline2.png", plot = p, width = 10, height = 5)

# Check Gene Diffusion on Cell graph by time
pl = lapply(1:length(genes),function(i){
  gene = genes[i]
  FeaturePlot_diffusion(coord = visual_space,init_state = rho[gene,],P_ls = P_ls,W = W,check_time = check_time,gene_name = NULL, gene_color = scales::hue_pal()(2)[i])
})
p = as.ggplot(pl[[1]]) / as.ggplot(pl[[2]] & labs(title = NULL))
ggsave(filename = "fig-pipeline3.png", plot = p, width = 16, height = 8)
```

@@

# Set the color code for all methods
method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_default","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v4 default", "Seurat v4 Wilcoxon unfiltered","HVGs"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(9, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
path = "./benchmark_result/"
tissue_ls = c("marrow_facs","pancreas_facs","lung_facs")
df_auc = do.call(rbind,lapply(tissue_ls,function(tissue_name){df = read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE); df$'Tissue' = tissue_name; df$'Method' = method_fullname[df$'Method']; df}))

df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1 - CellMarkerDB","Criterion2 - MaxFC")
df_auc$Tissue = factor(df_auc$Tissue,levels = tissue_ls)
levels(df_auc$Tissue) = c("Bone Marrow","Pancreas","Lung")
# Create the plot
fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 1), vjust = -0.25, size = 2.5, angle = 45) +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method]) + facet_wrap(~gt_set)
fig = fig + theme(
          legend.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          panel.grid = element_blank(),
          axis.line = element_line(colour = "black"),
          panel.background = element_blank(),
          strip.background = element_rect(fill = "white", color = "white") ,
          strip.text = element_text(size = 15, color = "black"))

ggsave(filename = "fig-known_marker_comparison.png", plot = fig, width = 8, height = 5)
```

# Fig - Gene Ranking Comparisons between LMD and Other Methods
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
# df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
#   paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
# })
g = c("Cd19","Naaa","Mogat2","Tifa","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
names(g) = rep(method_vs_set,each = 2)
pl = lapply(1:length(g),function(i){
  x = g[i]
  subtitle = sprintf("%s:%d, %s:%d",method_fullname[method_vs],df_label_all[x,method_vs],method_fullname[names(g)[i]],df_label_all[x,names(g)[i]])
  color_label = ifelse(df_label_all[x,method_vs] > df_label_all[x,names(g)[i]],"blue","red")
  FeaturePlot(tiss,features = x,order =TRUE) + labs(color = "Expression") + labs(title = x,subtitle = subtitle) + 
    theme(
      plot.title = element_text(face="bold", size = 30,color = color_label),
      plot.subtitle = element_text(size = 20),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      axis.line = element_blank())
  # + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
pl = pl[order(seq(length(g))%%2,decreasing = TRUE)]
pl[[1]] = pl[[1]] + labs(y = "Favored by LMD") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "red"))
pl[[(length(pl)/2)+1]] = pl[[(length(pl)/2)+1]] + labs(y = "Favored by Other methods") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "blue"))

@@

ggsave(filename = "fig-ranking_comparison2.png", plot = fig, width = 25, height = 10)

write.csv(df_label_all,file = "./marrow_result/gene_rank_comparison.csv",row.names = TRUE)
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  fullmethod = method_fullname[method]
  fullmethodvs = method_fullname[method_vs]
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = fullmethod
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = fullmethodvs
  df_label$'color' = factor(df_label$'color',levels = c(fullmethodvs,fullmethod))
  rank_cor = stats::cor(log(df_label[,1:2],base = 10),method = "pearson")[1,2]
  colnames(df_label)[1:2] = c("x","y")
  p = ggplot(df_label, aes(x=x, y=y,color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red","blue","grey50"),
                     breaks = c(fullmethodvs,fullmethod),
                     labels = c("Favored by LMD","Favored by Other methods")) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + 
    scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) + 
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), 
         y = paste0(method_fullname[method_vs]," Rank"),
         color = "Highlighted Genes",
         title = paste("cor =", round(rank_cor, 2)))
  # annotate gene labels
  p = p + ggrepel::geom_text_repel(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label),min.segment.length = unit(0, 'lines'),nudge_y = -0.5,show.legend = FALSE,size = 5)
  p = p + theme(
    plot.title = element_text(size = 15),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
})
for(i in 2:length(pl_rank)){
  pl_rank[[i]] <- pl_rank[[i]] + theme(axis.title.y=element_blank())
}
p = (wrap_plots(pl_rank,nrow = 1) & theme(legend.position="bottom")) + plot_layout(guides = "collect")

@@

# Fig - Density Index
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"
score_measure = read.table(paste0(path,tissue_name,"_density_index.csv"),header = TRUE)
score_measure = score_measure %>% filter(Method!="wilcox_no_filter")
score_measure$Method = ifelse(score_measure$Method %in% names(method_fullname),method_fullname[score_measure$Method],score_measure$Method)

@@

score_measure$'color' = coldef[score_measure$Method]
score_measure[score_measure$Method == "All genes","color"] = "black"
score_measure$'line_type' = "solid"
score_measure[score_measure$Method == "All genes","line_type"] = "dashed"

score_measure[grepl("Seurat",score_measure$Method),"Method"] = "Seurat v4"

# line_type = replace(coldef,names(coldef),"solid")
# line_type["Seurat v4 Wilcoxon unfiltered"] = "twodash"
# line_type["All genes"] = "dashed"

fig = ggplot(score_measure %>% filter(Method!="All genes") %>% filter(TopGene >= 100), aes(x = TopGene, y = DensityIndex, color = Method, group = Method, linetype = Method),linewidth = 2) + 
  geom_line(lwd = 1) +
  scale_x_log10(breaks = 10^(2:4), labels = expression(10^2, 10^3, 10^4)) +
    # expand_limits(x = c(50, 10^4)) +
  geom_hline(aes(yintercept = baseline, color = "All genes", linetype = "All genes")) +
  scale_color_manual(values = score_measure[,c("Method","color")] %>% distinct() %>% tibble::deframe()) + 
  scale_linetype_manual(values = score_measure[,c("Method","line_type")] %>% distinct() %>% tibble::deframe()) +
  theme(
    legend.title = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    legend.justification = 1,
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
  # geom_text_repel(data = score_measure %>%  filter(Method!="all genes") %>% group_by(Method) %>% slice_head(n = 2) %>% slice_tail(n = 1), aes(label = Method), hjust = 0)

ggsave(filename = "fig-densityindex.png", plot = fig, width = 5, height = 5)
```

@@

pl = lapply(list(jaccard_index,jaccard_index_droplet),function(mtx){
  jaccard_index_pruned = mtx[ct_selected,module_selected]
  colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
  Visualize_jaccard_mtx(jaccard_index_pruned)
})
titles = c("FACS","Droplet")
pl <- lapply(1:length(pl), function(i){pl[[i]] + labs(title = titles[i]) + theme(plot.title = element_text(size = 20, face = "bold"))})
p = wrap_plots(pl,ncol = 2) + plot_layout(guides = "collect")
ggsave(filename = "supfig-ct-specific-module3.png", plot = p, width = 10, height = 8)
```
# Fig - Cell Cycle
## Annotate CC
```{r}
cell_cycle = read.csv("./marrow_result/annotated_cell_cycle.csv")
tiss$'Phase' = cell_cycle %>% filter(Dataset == "FACS") %>%.$Phase
tiss$Phase = factor(tiss$Phase,levels = c("G1","S","G2M"))
p1 = DimPlot(tiss,group.by = "Phase", cols = c("grey",scales::hue_pal()(3)[3:2])) + labs(title = "Phase annotated by Seurat",color = "Phase") + theme(
  plot.title = element_text(size = 10),
  axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.line = element_blank())
tiss_droplet$'Phase' = cell_cycle %>% filter(Dataset == "Droplet") %>%.$Phase
tiss_droplet$Phase = factor(tiss_droplet$Phase,levels = c("G1","S","G2M"))
p2 = DimPlot(tiss_droplet,group.by = "Phase", cols = c("grey",scales::hue_pal()(3)[3:2])) + labs(title = "Phase annotated by Seurat",color = "Phase") + theme(
  axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.line = element_blank())

cc_module = c(32,31,18)
pl_module_cc = lapply(cc_module,function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
pl_module_cc_droplet = lapply(cc_module,function(module){
  FeaturePlot_custom(value = cell_block_droplet[,module], coord = data.frame(tiss_droplet@reductions$tsne@cell.embeddings), value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
p = wrap_plots(p1,wrap_plots(pl_module_cc,ncol = 3) & theme(plot.title = element_text(size = 15)) ,p2 + labs(title = NULL),wrap_plots(pl_module_cc_droplet,ncol = 3) & theme(plot.title = element_text(size = 15)) & labs(title = NULL),nrow = 2,design = "ABBB\nCDDD") + plot_layout(guides = "collect")

ggsave(filename = "fig-module-cellcycle1.png", plot = p, width = 3*4 + 1, height = 3*2)
```
## Reactome enrichment
```{r}
df = read.csv("./marrow_result/reactome_pathway_cc.csv")
df = df %>% filter(module %in% cc_module)
df$GeneRatio = unlist(lapply(df$GeneRatio,function(x) eval(parse(text = x))))
# df$GeneRatio = as.numeric(df$Count / table(gene_partition)[df$module])
Description_order = levels(factor(df$Description))
Description_order = rev(Description_order[order(match(Description_order,c("Cell Cycle","Cell Cycle, Mitotic","Mitotic G1 phase and G1/S transition","G1/S Transition","S Phase","M Phase","DNA Replication","Mitotic Prometaphase")))])
df$Description = factor(df$Description,levels = Description_order) 
df$module = factor(df$module,levels = c(32,31,18))

p = ggplot(df, aes(x=module, y=Description)) +
  geom_point(aes(size=GeneRatio, color=p.adjust), alpha=0.7) +
  scale_color_gradientn(colors=colorRampPalette(c("red", "blue"))(99), name="p.adjust",limits = c(0,0.05)) +
  theme_minimal() +
  labs(size="Gene Ratio",x = "Module") +
  theme(legend.position="right",
        axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
      axis.text.y = element_text(size = 10),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15))
ggsave(filename = "fig-module-cellcycle2.png", plot = p, width = 10, height = 6)
```
